Topic categorization in Portuguese news articles\\ \thanks{Fundação para a Ciência e Tecnologia}

### 2018-01-03 article.tex
References and cheating table spaces to fit

In addition to the document content (for example, in a news article,
the \emph{title}, \emph{lead} and \emph{body}), its metadata is also
important: author(s), date of publication, source, topic, mentioned
entities and their relations, etc. Some of this metadata might be
filled in and stored along with the document (e.g. \emph{author} and
\emph{date of publication}); other is usually extracted from the
document content (e.g. mentioned entities).

An example of a feature which improves information access is the
categorization of news articles by the topic (or topics) of its
content\cite{kim2006extracting}. The presence of such a categorization
may influence the way the information is stored, organized, displayed
and queried.

@@

\begin{table}[htbp]
    \caption{Lists size}
\begin{center}
\begin{tabular}{l|SS}
    & \parbox{6em}{\centering Sparsity\\threshold (\%)}  &
    \parbox{5em}{\centering Number\\of terms}   \\\hline
    $LT_{90}$ &  90                 &  45 \\
    $LT_{95}$ &  95                 & 139 \\
    $LT_{99}$ &  99                 & 912 \\
\end{tabular}
\label{tab:size}
\end{center}
\end{table}

@@

\begin{table}[htbp]
    \caption{Execution times for training}
\begin{center}
\begin{tabular}{l|cr}
    & Algorithm  & \parbox{3em}{\centering Training\\time} \\\hline
    $LT_{90}$    & DT         & 12s  \\
    $LT_{95}$    & KNN        &  3m  \\
    $LT_{99}$    & KNN        & 57m  \\
\end{tabular}
\label{tab:exectime}
\end{center}
\end{table}

@@

\begin{table}[htbp]
    \caption{Error rates}
\begin{center}
\begin{tabular}{l|rrrrrr}
                 & DT            & KNN           & NB   & NN   & SVM\textsubscript{RK} & SVM\textsubscript{LK} \\ \hline
    $LT_{90}$    & \textbf{0.60} & 0.71          & 0.85 & 0.61 & 0.88                  & 0.88                  \\
    $LT_{95}$    & 0.70          & \textbf{0.56} & 0.83 & 0.58 & 0.87                  & 0.87                  \\
    $LT_{99}$    & 0.70          & \textbf{0.35} & 0.87 & 0.76 & 0.87                  & 0.87                  \\
\end{tabular}
\label{tab:error}
\end{center}
\end{table}

>>>>

In addition to the document content (for example, in a news article,
the \emph{title}, \emph{lead} and \emph{body}), its metadata is also
important: author(s), date of publication, source, topic, mentioned
entities and their relations, etc\cite{yaginuma2003metadata,yaginuma2003design}. Some of
this metadata might be filled in and stored along with the document
(e.g. \emph{author} and \emph{date of publication}); other is usually
extracted from the document content (e.g. mentioned
entities)\cite{vadrevu2005automated}.

An example of a feature which improves information access is the
categorization of news articles by the topic (or topics) of its
content\cite{kim2006extracting}. The presence of such a categorization
may influence the way the information is stored, organized, displayed
and queried\cite{teitler2008newsstand}.

@@

\begin{table}[htbp]
    \vspace{-.5cm}
    \caption{Lists size}
\begin{center}
\begin{tabular}{l|SS}
    & \parbox{6em}{\centering Sparsity\\threshold (\%)}  &
    \parbox{5em}{\centering Number\\of terms}   \\\hline
    $LT_{90}$ &  90                 &  45 \\
    $LT_{95}$ &  95                 & 139 \\
    $LT_{99}$ &  99                 & 912 \\
\end{tabular}
\label{tab:size}
\end{center}
\end{table}

@@

\begin{table}[htbp]
    \vspace{-.2cm}
    \caption{Execution times for training}
\begin{center}
\begin{tabular}{l|cr}
    & Algorithm  & \parbox{3em}{\centering Training\\time} \\\hline
    $LT_{90}$    & DT         & 12s  \\
    $LT_{95}$    & KNN        &  3m  \\
    $LT_{99}$    & KNN        & 57m  \\
\end{tabular}
\label{tab:exectime}
\end{center}
\end{table}

@@

\begin{table}[htbp]
    \vspace{-.2cm}
    \caption{Error rates}
\begin{center}
\begin{tabular}{l|rrrrrr}
                 & DT            & KNN           & NB   & NN   & SVM\textsubscript{RK} & SVM\textsubscript{LK} \\ \hline
    $LT_{90}$    & \textbf{0.60} & 0.71          & 0.85 & 0.61 & 0.88                  & 0.88                  \\
    $LT_{95}$    & 0.70          & \textbf{0.56} & 0.83 & 0.58 & 0.87                  & 0.87                  \\
    $LT_{99}$    & 0.70          & \textbf{0.35} & 0.87 & 0.76 & 0.87                  & 0.87                  \\
\end{tabular}
\label{tab:error}
\end{center}
\end{table}
